\documentclass[margin,line,article,letterpaper]{res}
%\allsectionsfont{\sffamily}
\usepackage{bibentry}
\usepackage{url}
\usepackage{verbatim}
\usepackage{revnum}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in


\newenvironment{noindentlist}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0in}}}{\end{list}}

\newenvironment{list1}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}

\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcommand{\timespan}[1]{#1}

\newcommand{\showpaper}[1]{\item \bibentry{#1}}

\begin{document}
\bibliographystyle{myacm}
\nobibliography{bird}

\name{Christian Bird\vspace*{.1in}}

\begin{resume}
\section{Contact Information}
\vspace{.05in}
One Microsoft Way\\
Building 99/2227\\
Redmond, WA 98052\\
{\it E-mail:}  cbird@microsoft.com\\
\url{http://www.cabird.com}
 
\section{Research \\
Interests}
Empirical software engineering, Open Source Software communities, social networks, 
communication and collaboration in software engineering, software tools

\section{Education}
\textbf{University of California, Davis}, Davis, California, USA
\begin{list1}
\item Ph.D., Computer Science, June 2010
\begin{list2}
\vspace*{.05in}
\item Dissertation Topic:  ``Sociotechnical Collaboration and Coordination in Open Source Software'' 
\item Advisor:  Prof. Premkumar Devanbu
\item GPA: 3.98
\end{list2}
\end{list1}

\textbf{University of California, Davis}, Davis, California, USA
\begin{list1}
\item M.S., Computer Science, 2008
\begin{list2}
\vspace*{.05in}
\item Advisor:  Prof. Premkumar Devanbu
\item GPA: 3.98
\end{list2}
\end{list1}

\textbf{Brigham Young University}, Provo, Utah, USA
\begin{list1}
\item Bachelor of Science in Computer Science, 2003
\begin{list2}
\vspace*{.05in}
\item GPA : 3.78
\end{list2}
\end{list1}


\section{Honors and Awards} 

ACM SIGSOFT Distinguished Paper and ISSTA Best Paper
\begin{list2}
\item ACM SigSoft International Symposium on Software Testing and Analysis, ``Collecting a Heap of Shapes'', 2013
\end{list2}

Distinguished Referee
\begin{list2}
\item ACM Transactions on Software Engineering and Methodology, 2011-2012
\end{list2}

ACM SIGSOFT Distinguished Paper
\begin{list2}
\item ACM SigSoft Symposium on Foundations of Software Engineering, ``Assessing the Value of Branches with What-If Analysis'', 2012
\end{list2}

ACM SIGSOFT Distinguished Paper
\begin{list2}
\item International Conference on Software Engineering, ``Does Distributed Development
Affect Software Quality?  An Empirical Case Study of Windows Vista'', 2009
\end{list2}

Mining Software Repositories Best Paper Award
\begin{list2}
\item International Working Conference on Mining Software Repositories, ``Clones: What \emph{is} that smell?'', 2010
\end{list2}

Best Student Talk
\begin{list2}
\item Mining Software Archives, ``The Effect of Change Semantics on Coordination Requirements'', 2010
\end{list2}

Best Graduate Researcher Award
\begin{list2}
\item U.C. Davis, Dept. of Computer Science, 2008 -- 2009
\end{list2}


Brigham Young University Dean's List
\begin{list2}
\item Awarded in 1996, 2001, 2002
\end{list2}

Golden Key Honor Society
\begin{list2}
\item Member, 2000 -- present
\end{list2}

US National Merit Scholar and Scholarship
\begin{list2}
\item Awarded in 1996 for complete undergraduate career.
\end{list2}

\vspace{20pt}

\section{Refereed Publications}

\begin{revnumerate}[46]

\showpaper{nagappan2013diversity}

\showpaper{rigby2013convergent}

\showpaper{murphy2013agile}

\showpaper{barr2013shapes}

\showpaper{musson2013software}

\showpaper{harper2013ecscw}

\showpaper{bacchelli2013eoc}

\showpaper{murphyhill2013dbf}

\showpaper{kocaguneli2013distributed}

\showpaper{rigby2013releng}

\showpaper{mukadam2013gerrit}

\showpaper{smith2013chase}

\showpaper{parnin2012auj}

\showpaper{bird2012avb}

\showpaper{hindle2012rri}

\showpaper{shihab2012ebs}

\showpaper{bird2012www}

\showpaper{barr2012cid}

\showpaper{zimmermann2012ccs}

\showpaper{rahman2012cwt}

\showpaper{menzies2011ise}

\showpaper{zeller2011ffl}

\showpaper{hong2011uds}

\showpaper{bird2011dtm}

\showpaper{parnin2011jga}

\showpaper{bird2011tbg}

\showpaper{posnett2010esi}

\showpaper{barr2010sg}

\showpaper{bachmann2010mlb}

\showpaper{posnett2010tmm}

\showpaper{nia2010vna}

\showpaper{rahman2010cws}

\showpaper{bird2009pat}

\showpaper{bird2009fbb}

\showpaper{bird2009dddb}

\showpaper{bird2009ddd}

\showpaper{bird2009ppm}

\showpaper{bird2009sdr}

\showpaper{bird2008lss}

\showpaper{pattison2008twp}

\showpaper{saul2007rrw}

\showpaper{bird2007dps}

\showpaper{bird2007obi}

\showpaper{ogawa2007vsi}

\showpaper{bird2006mes}

\showpaper{bird2006mesp}

\end{revnumerate}

\section{Book Chapters}


\begin{revnumerate}[1]

\showpaper{bird2010cc}

\end{revnumerate}

\section{Invited Papers, Demo papers, etc.}

\begin{revnumerate}[4]

\showpaper{bird2011scc}

\showpaper{bird2011ese}

\showpaper{rahman2010cws-esem}

\showpaper{bird2010lee}

\end{revnumerate}


\section{Invited Talks}

Branch Analytics at Microsoft \hfill \timespan{November, 2012}\\
\vspace{-10pt}
\begin{list1}
\item University of Victoria
\item Victoria, British Columbia, Canada
\end{list1}

Empirical Software Engineering at Microsoft Research: Transitioning Research into practice \hfill \timespan{September, 2011}\\
\vspace{-10pt}
\begin{list1}
\item Brigham Young University
\item Provo, Utah, U.S.A.
\end{list1}


SocioTechnical Effects in Software Teams \hfill \timespan{April, 2011}\\
\vspace{-10pt}
\begin{list1}
\item Hong Kong University of Science and Technology
\item Hong Kong
\end{list1}

SocioTechnical Effects in Software Teams \hfill \timespan{February, 2010}\\
\vspace{-10pt}
\begin{list1}
\item Microsoft Research
\item Bangalore, India
\end{list1}

Does Distributed Development Affect Software Quality? \hfill \timespan{February, 2010}\\
\vspace{-10pt}
\begin{list1}
\item Third India Software Engineering Conference
\item Mysore, India
\end{list1}

Jazz Anthropology \hfill \timespan{January, 2010}\\
\vspace{-10pt}
\begin{list1}
\item T. J. Watson Research Center, IBM
\item Hawthorne, New York, U.S.A.
\end{list1}

On the Effect of Ownership in Varying Software Processes \hfill \timespan{September, 2009}\\
\vspace{-10pt}
\begin{list1}
\item Microsoft Research
\item Redmond, Washington, U.S.A.
\end{list1}

Latent Social Structure in Open Source Projects \hfill \timespan{October, 2008}\\
\vspace{-10pt}
\begin{list1}
\item INFORMS Annual Meeting
\item Washington, D.C., U.S.A.
\end{list1}

Does Distributed Development Affect Software Quality? \hfill \timespan{August, 2008}\\
\vspace{-10pt}
\begin{list1}
\item Microsoft Research
\item Redmond, Washington, U.S.A.
\end{list1}

Social Organization in Open Source Software \hfill \timespan{March, 2008}\\
\vspace{-10pt}
\begin{list1}
\item T. J. Watson Research Center, IBM
\item Hawthorne, New York, U.S.A.
\end{list1}

Social Network Analysis in Software Teams \hfill \timespan{May, 2006}\\
\vspace{-10pt}
\begin{list1}
\item Guest Lecture, MAE 298, Understanding Networks: Theory and Applications
\item University of California, Davis, U.S.A.
\end{list1}

\section{Research Experience}

\textbf{Researcher} \hfill \timespan{October, 2011 -- present}\\
\vspace{-10pt}
\begin{list1}
\item Empirical Software Engineering Group
\item Microsoft Research
\item Redmond, Washington, USA
\vspace{6pt}
\item  
\end{list1}


\textbf{Postdoctoral Researcher} \hfill \timespan{August, 2010 -- October, 2011}\\
\vspace{-10pt}
\begin{list1}
\item Empirical Software Engineering Group
\item Microsoft Research
\item Redmond, Washington, USA
\vspace{6pt}
\item  
\end{list1}

\textbf{Research Assistant} \hfill \timespan{October, 2005 -- June, 2010}\\
\vspace{-10pt}
\begin{list1}
\item Software Engineering under Prof. Premkumar Devanbu
\item University of California, Davis,
\item Davis, California, USA
\vspace{6pt}
\item Designed and implemented data mining software for study of OSS projects. Statistically 
analyzed OSS project data in the fields of social networking, change analysis, 
longitudinal social effects, acceptance of work gifts, etc. Continued background research in the 
area of empirical software engineering.
\end{list1}

\textbf{Researcher} \hfill \timespan{November 2009 -- January 2010}\\
\vspace{-10pt}
\begin{list1}
\item Governance Science Research Group under Clay Williams
\item T. J. Watson Research Center, IBM
\item Hawthorne, New York, USA
\vspace{6pt}
\item Developed a research amenable database schema for Jazz development
    data and implemented a mining framework for extracting relevant development
    data from Jazz repositories.
\end{list1}


\textbf{Researcher} \hfill \timespan{June -- September 2009}\\
\vspace{-10pt}
\begin{list1}
\item Research in Software Engineering Group under Nachiappan Nagappan
\item Microsoft Research
\item Redmond, Washington, USA
\vspace{6pt}
\item Examined the effect of code ownership levels on software quality in various
	development contexts, including Windows Vista, Eclipse, and Firefox.  Also
	examined distributed development in the context of different development
	process domains.  This research resulted in an internal report, an external
	tech report, and two planned submissions to FSE 2010.
\end{list1}

\textbf{Researcher} \hfill \timespan{May -- August 2008}\\
\vspace{-10pt}
\begin{list1}
\item Research in Software Engineering group under Nachiappan Nagappan
\item Microsoft Research
\item Redmond, Washington, USA
\vspace{6pt}
\item Conducted quantitative analysis on defect data related to development of Windows 
Vista and examined many sociotechnical factors and their relationship with defects. 
Examined the effect of geographical distributed development on software quality which 
resulted in a top tier publication at ICSE, earned a best paper award at ICSE,
and was invited to appear in CACM Research Highlights.  Also performed a study
of the ability of network measures on sociotechnical networks to predict failures,
which resulted in a paper in ISSRE.
\end{list1}

\textbf{Research Assistant} \hfill \timespan{June -- October, 2005}\\
\vspace{-10pt}
\begin{list1}
\item Software Engineering under Prof. Raju Pandey
\item University of California, Davis,
\item Davis, California, USA
\vspace{6pt}
\item Worked on a framework for component oriented binary level synthesis for embedded 
systems. Wrote a static analysis tool for extracting type dependencies in GCC compliant 
C. 
\end{list1}

\section{Teaching Experience}
\textbf{Teaching Assistant} \hfill \timespan{October, 2004 -- June, 2005}\\
\vspace{-10pt}
\begin{list1}
\item Programming Languages under Dr. Ron Olsson and Dr. Raju Pandey
\item University of California, Davis
\item Davis, California, USA
\vspace{6pt}
\item Led discussion sections of senior level programming languages course for three quarters.
Provided individual assistance to students during regularly scheduled office hours. 
Helped in the creation of homework assignments and exams. Evaluated students written 
work, programming projects, and exams. 
\end{list1}

\textbf{Teaching Assistant} \hfill \timespan{August, 1997 -- December, 1997}\\
\vspace{-10pt}
\begin{list1}
\item Advanced Data Structures under Dr. Theodore Norman
\item Brigham Young University
\item Provo, Utah, USA
\vspace{6pt}
\item Helped students understand advanced data structure concepts in group and one on one 
settings. Evaluated course homework, lab projects, and exams. 
\end{list1}



\section{Industry Experience}
\textbf{Software Engineer} \hfill \timespan{September, 2000 -- December, 2005}\\
\vspace{-10pt}
\begin{list1}
\item Embedded Software Tools Group under Bruce Vernon
\item Motorola
\item Lindon, Utah, USA
\vspace{6pt}
\item Helped design and develop command line and GUI tools for embedded linux developers
using C, C++, python, and shell scripting. Aided in the creation of linux Board 
Support Packages for embedded hardware on a number of Motorola's hardware platforms. 
Maintained a collaborative intranet web system for the embedded linux group. 
Provided remote and on-site training to Motorola employees and third parties in the 
use of our tools. 
\end{list1}

\textbf{Technical Support Engineer} \hfill \timespan{August - December, 1997}\\
\vspace{-10pt}
\begin{list1}
\item Technical Support Department under Allen Smart
\item Caldera Systems Inc.
\item Provo, Utah, USA
\vspace{6pt}
\item Learned advanced Linux operating system and programming concepts. Provided technical

support to corporate customers for their use of Linux. Helped design an efficient 
techincal support structure for a rapidly growing Linux technology company.
\end{list1}


\section{Academic \hspace{.2in} Service}
\textbf{Reviewer}
\begin{list1}
\item Communications of the ACM, 2010
\item ACM Transactions on Software Engineering and Methodology, 2009, 2010, 2011, 2012, 2013
\item IEEE Transactions on Software Engineering, 2009, 2010, 2011, 2012
\item IEEE Software, 2008, 2011, 2012, 2013
\item IEEE Intelligent Systems, 2009, 2010
\item Journal of Systems and Software, 2009, 2011, 2012
\item Journal of Information and Software Technology, 2009, 2011
\item Journal of Empirical Software Engineering, 2009, 2010, 2011, 2012
\item Journal of Software: Evolution and Process, 2012
\item Software Quality Journal, 2011
\item International Symposium on Software Testing and Analysis, 2012
\item International Conference on Software Engineering, 2008, 2009, 2013
\item ACM Conference on Computer Supported Cooperative Work, 2008, 2012, 2013
\item International Working Conference on Mining Software Repositories, 2007, 2008, 2009
\item European Conference on Object Oriented Programming, 2009
\item Haifa Verification conference, 2011
\item ACM Conference on Recommender Systems, 2009
\item Science of Computer Programming, 2011
\end{list1}

\textbf{Program Committee Memberships}
\begin{list1}
\item International Conference on Automated Software Engineering, 2014
\item International Conference on Software Engineering, 2014
\item International Symposium on Software Reliability Engineering, Industrial track, 2013
\item ACM Sigsoft Symposium on Foundations of Sofware Engineering, 2012
\item International Conference on Software Maintenance, 2012, 2013
\item International Conference on Program Comprehension, 2012
\item International Conference on Predictor Models in Software Engineering, 2013
\item International Conference on Software Engineering Advances, 2013
\item International Working Conference on Mining Software Repositories, 2010, 2011, 2012, 2013
\item ACM Student Research Competition (at ICSE), 2012
\item Formal Research Demonstrations track at ICSE, 2014
\item Int'l Symposium on Empirical Software Engineering and Measurement, Industrial track, 2011
\item International Conference on Software Maintenance, Early Achievements track, 2011
\item European Soft. Eng. Conf./Foundations of Soft. Eng., Artifact Evaluation Committee, 2011
\item Euromicro Conference on Software Engineering and Advanced Applications Special Session on Estimation and Prediction in Software \& Systems Engineering, 2012
\item 2nd SEMAT Workshop on a General Theory of Software Engineering (GTSE) 2013, 
\item International Workshop on Regression Testing, 2012, 2013
\item International Workshop on Machine Learning Technologies in Software Engineering, 2011
\item International Workshop on Empirical Software Engineering in Practice, 2010, 2011, 2012, 2013
\item International Workshop on Replications in Empirical Software Engineering Research, 2010, 2011
\item International Workshop on Emerging Trends in FLOSS Research and Development, 2010
\item International Workshop on the General Theory of Software Engineering, 2013
\item Challenge Track of Mining Software Repositories, 2008, 2009
\end{list1}

\textbf{Program Committee Chair Positions}
\begin{list1}
\item International Workshop on Replications in Software Engineering, 2013
\item International Workshop on Data Analysis Patterns in Software Engineering (DAPSE), 2013
\item International Workshop on Release Engineering (RelEng), 2013
\item International Conference on Program Comprehension, Industry Track (co-chair), 2013
\item Challenge Track of Mining Software Repositories, 2009
\end{list1}

\textbf{Organizing Committee Positions}
\begin{list1}
\item International Workshop on Data Analysis Patterns in Software Engineering (DAPSE), 2013
\item International Workshop on Release Engineering (RelEng), 2013
\item International Workshop on Replications in Software Engineering, 2013
\end{list1}

\textbf{Conference Service}
\begin{list1}
\item Student Volunteer Chair, Sigsoft Sympsium on Foundations of Software Engineering, 2014
\end{list1}

\textbf{Thesis Committees}
\begin{list1}
\item Adrian Schr\"{o}ter, Ph.D., University of Victoria, 2012
\end{list1}

\section{Memberships}
\begin{noindentlist}
\item Member, Institute of Electrical and Electronics Engineers (IEEE) \hfill 2005--present
\item Member, ACM Special Interest Group on Software Engineering (SIGSOFT) \hfill 2005--present
\end{noindentlist}



\begin{comment}
I don't think anyone cares about this
\section{Technical Skills} 
\begin{list2}
\item Proficient:  C, Java, Python, C++, PostgreSQL, MySQL, Ruby, R, \LaTeX
\item Familiar: Lisp, Prolog, C\#, SML
\end{list2}
\end{comment}

\section{Extracurricular}
Software Engineering and Programming Languages Seminar Organizer \hfill \timespan{2006--2008}

\section{References}

Premkumar Devanbu
\begin{list1}
\item Professor
\item University of California, Davis
\item Dept. of Computer Science
\item Kemper Hall
\item 1 Shields Avenue
\item Davis, CA, USA 95616
\item \texttt{ptdevanbu@ucdavis.edu}
\end{list1}

Nachiappan Nagappan
\begin{list1}
\item Researcher
\item Microsoft Research
\item One Microsoft Way
\item Redmond, WA, USA 98052
\item \texttt{nachin@microsoft.com}
\end{list1}

Harald Gall
\begin{list1}
\item Professor
\item University of Z\"urich
\item Dept. of Computer Science
\item Binzm\"uhlestrasse 14
\item CH-8050 Z\"urich, Switzerland
\item \texttt{gall@ifi.uzh.ch}
\end{list1}

James Herbsleb
\begin{list1}
\item Professor, Institute for Software Research
\item Director, Software Industry Center
\item School of Computer Science
\item 5321 Wean Hall
\item Carnegie Mellon University
\item 5000 Forbes Avenue
\item Pittsburgh, PA 15213
\item \texttt{jdh@cs.cmu.edu}
\end{list1}

Audris Mockus
\begin{list1}
\item Researcher
%\item Software Technology Research Department
\item Avaya Labs Research
\item Rm 2D-30
\item 233 Mt. Airy Road
\item Basking Ridge, NJ 07920
\item \texttt{audris@research.avayalabs.com}
\end{list1}

\end{resume}
\end{document}
