\documentstyle[margin,line]{res}

\renewcommand{\namefont}{\Large}
\newcommand{\secft}{\bf}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in


\pdfcompresslevel=0             %-- 0 = none, 9 = best
\pdfinfo{                       %-- Info dictionary of PDF output
  /Author (Christian Alma Bird)
  /Title (Curriculum Vitae)
  /Subject (Curriculum Vitae)
  /Keywords ()
  /Creator (pdfLaTeX)
}
\pdfcatalog{          %-- Catalog dictionary of PDF output.
  %/PageMode
  %/UseNone
  %/UseOutlines
  %/UseThumbs
  %/FullScreen
  /URI (http://wwwcsif.cs.ucdavis.edu/~bird)
} openaction goto page 1 {/Fit}

\begin{document}


\name{Christian A. Bird}
\address{2249 Kemper Hall\\
University of California, Davis\\
Davis, CA 95616}

\address{bird@cs.ucdavis.edu\\
http://wwwcsif.cs.ucdavis.edu/$\sim$bird/
}

\begin{resume}

\begin{format}
\title{l}\dates{r}\\
\location{l}\employer{r}\\
\body\\
\end{format}

\section{\secft Education}

\title{\em Ph.D. Graduate Student in Computer Science}
\dates{\bf 2004 -- Present}
\location{University of California, Davis}
\employer{}
\begin{position}
GPA: 3.96 
\end{position}

\title{\em M.S. in Computer Science}
\dates{\bf 2008}
\location{University of California, Davis}
\employer{}
\begin{position}
GPA: 3.96 
\end{position}

\title{\em B.S. in Computer Science}
\dates{\bf 1996 -- 1998}
\employer{\bf 2000 -- 2003}
\location{Brigham Young University, Provo, UT}
\begin{position}
GPA: 3.8
\end{position}

\section{\secft Interests} Open Source Software communities, social networks, empirical software engineering, communication \& collaboration in software engineering, programming languages, domain specific languages, software tools

%\section{\secft Objective}

% \section{\secft Objective} A research internship in any of: program analysis, web
% application security, and software engineering.

\section{\secft Honors and Awards}
\begin{tabular} {@{}l@{\hspace{3cm}}l}
National Merit Scholar (and scholarship) &
Golden Key Honor Society \\
Dean's List 1996, 2001, 2002 &
 
\end{tabular}



\section{\secft Publications}

C.\ Bird, E.\ Barr, A.\ Nash, P.\ Devanbu, V.\ Filkov, Z.\ Su
``Structure and Dynamics of Research Collaboration in Computer Science,''
{\em SIAM International Conference on Data Mining}, 2009

C.\ Bird, N.\ Nagappan, P.\ Devanbu, H.\ Gall, B.\ Murphy
``Does Distributed Development Affect Software Quality? An Empirical Case Study of Windows Vista,''
{\em International Conference on Software Engineering}, 2009

C.\ Bird, D.\ Pattison, R.\ D`Souza, V.\ Filkov, and P.\ Devanbu 
``Latent Social Structure in Open Source Projects,''
{\em ACM SIGSOFT Foundations of Software Engineering}, 2008

D.\ Pattison, C.\ Bird, and P.\ Devanbu,
``Talk \& Work: A preliminary report,'' 
{\em 5th Annual Working Conference on Mining Software Repositories},
2007

Z.\ Saul, V.\ Filkov, P.\ Devanbu, and C.\ Bird,
``Recommending Random Walks'' (nominated for Best Paper award),
{\em ACM ESEC/SIGSOFT Foundations of Software Engineering}, 2007

C.\ Bird, A.\ Gourley, P.\ Devanbu, A.\ Swaminathan, and G.\ Hsu,
``Open Borders? Immigration in Open Source Projects,'' 
{\em 4th Annual Workshop on Mining Software Repositories},
2007

C.\ Bird, A.\ Gourley, and P.\ Devanbu,
``Detecting Patch Submission and Acceptance in OSS Projects,'' 
{\em 4th Annual Workshop on Mining Software Repositories},
2007

M.\ Ogawa, K-L.\ Ma, C.\ Bird, P.\ Devanbu, A.\ Gourley,
''Visualizing Social Interaction in Open Source Software Projects'',
{\em Asia Pacific Symposium on Visualisation},
2007

C.\ Bird, A.\ Gourley, P.\ Devanbu, M.\ Gertz, and A.\ Swaminathan,
``Mining Email Social Networks,''
{\em 3rd Annual Workshop on Mining Software Repositories},
2006

C.\ Bird, A.\ Gourley, P.\ Devanbu, M.\ Gertz, and A.\ Swaminathan,
``Mining Email Social Networks in Postgres,''
{\em 3rd Annual Workshop on Mining Software Repositories Mining Challenge},
2006

\section{\secft Professional Activities}

Program Committee, {\em 5th Annual Working Conference on Mining Software Repositories}, 
Challenge Track, 2008

\section{\secft Research and Work Experience}

\begin{format}
\title{l}\employer{r}\\
\location{l}\advisor{r}\\
\dash{l}\dates{r}\\
\body\\
\end{format}

\title{\em Research Assistant}
\advisor{\bf Dr.\ Premkumar Devanbu}
\employer{\bf University of California, Davis}
\dates{\bf Oct.\ 2005 -- Present}
\location{\em Software Engineering}
\dash{\quad ---}
\begin{position}
Designed and implemented data mining software for study of OSS projects.
Statistically analyzed OSS project data in the fields of social networking,
change analysis, longitudinal social effects, acceptance of work gifts, etc.
Continued background research in the area of empirical software engineering
\end{position}


\title{\em Teaching Assistant}
\advisor{\bf Dr. Ronald Olsson, Dr. Raju Pandey}
\employer{\bf University of California, Davis}
\dates{\bf Sept.\ 2004 -- June 2005}
\location{\em Programming Languages}
\begin{position}
Led discussion sections of senior level programming languages course for
three quarters.
Provided individual assistance to students during regularly scheduled
office hours.  Helped in the creation of homework assignments and exams.
Evaluated students written work, programming projects,
and exams.
\end{position}



\title{\em Software Engineer}
\advisor{\bf Bruce Vernon}
\employer{\bf Motorola}
\dates{\bf  Sept.\ 2000 --  Dec.\ 2005}
\location{\em Embedded Software Tools Group}
\begin{position}
Helped design and develop command line and GUI tools for 
embedded linux developers using C,
C++, python, and shell scripting. Aided in the creation
of linux Board Support Packages for embedded hardware on
a number of Motorola's hardware platflorms.  
Maintained a collaborative intranet web system for the
embedded linux group.  Provided remote and on-site training to Motorola
employees and third parties in the use of our tools.
\end{position}

%\newpage

\title{\em Technical Support Engineer}
\advisor{\bf Allen Smart}
\employer{\bf Caldera Systems Inc.}
\dates{\bf Aug.\ -- Dec.\ 1997}
\location{\em Technical Support Department}
\begin{position}
Learned advanced Linux operating system and programming concepts.
Provided technical support to corporate customers for their
use of Linux. Helped design an efficient techincal support
structure for a rapidly growing Linux technology company
\end{position}


\title{\em Teaching Assistant}
\advisor{\bf Dr. Theodore Norman}
\employer{\bf Brigham Young University}
\dates{\bf Aug.\ -- Dec.\ 1997}
\location{\em Advanced Data Structures}
\begin{position}
Helped students understand advanced data structure concepts in group and 
one on one settings.  Evaluated course homework, lab projects, and exams.
\end{position}


\begin{format}
\location{l} \dates{r}\\
\body\\
\end{format}

%\location{\bf Architectural-Based Security Analysis.}
%\dates{\bf March 2005 -- Present.}
%\begin{position}
%In connection with Crandall et al.'s Minos and Dacoda's projects, I designed
%a weakest precondition-based technique to map out the time-dependent
%behavior of malicious code.
%\end{position}


\begin{format}
\title{l}\employer{r}\\
\dash{l}\advisor{r}\\
\location{l}\dates{r}\\
\body\\
\end{format}

% \begin{format}
%     \title{l}\dates{r}\\
% \employer{l}\\
% \advisor{l}\\
% \location{l}\\
% \body\\
% \end{format}

%\title{\em Engineering Intern}
%\employer{\bf Syneon, LLC}
%\advisor{\bf Chuck Taylor}
%\dash{\quad ---}
%\dates{\bf June 2001 -- Sept.\ 2001.}
%\location{\bf Complex Structures Design}
%\begin{position}
%I did background research and collaborated on 3D printing and 
%collapsable structures projects.
%\end{position}

%\title{\em Undergraduate Research}
%\employer{\bf UC Davis}
%\advisor{\bf Chip Martel}
%\dates{\bf June 2000 -- Sept.\ 2000.}
%\dash{\quad ---}
%\location{\bf Graph Disconnectivity}
%\begin{position}
%I contributed to an implementation of a graph disconnectivity algorithm for
%empiracle study.
%\end{position}

% \section{\secft Skills} Programming languages: C, C++, Java, OCaml, Python, PHP;
% Operating Systems: Debian and Redhat Linux, Windows XP; Tools and Systems:
% Flex, Bison, Tomcat, Apache, PHPSA, Doxygen.

%\section{\secft Teaching Experience}

%\begin{format}
%\title{l}\employer{r}\\
%\location{l}\dates{r}\\
%\body\\
%\end{format}

%\title{\em Teaching Assistant}
%\employer{\bf Department of Computer Science}
%\dates{\bf Sep. 2002 -- July 2003.}
%\location{UC Davis}
%\begin{position}
%I led discussion sections, guest lectured, graded homework, held office
%hours, and led review sessions for: {Computer Security}, {Software
%Engineering}, {Programming and Problem Solving} (three quarters).  
%\end{position}

\section{\secft Professional Organizations}
Member of Association for Computing Machinery (ACM) and ACM SIGSOFT\\
Member of IEEE Computer Society

\section{\secft Volunteer Service}
LDS Church Service Mission\\
Denver, Colorado\\
Jan.\ 1998 -- Feb.\ 2000

%\title{\em Church Service Mission}
%\advisor{\bf Conrad Schultz}
%\dates{\bf Jan.\ 1998 -- Feb.\ 2000}
%\employer{\bf LDS Church}
%\location{\em Denver, Colorado}
%\begin{position}
%stuff
%\end{position}

%\section{\secft Citizenship} USA

\section{\secft References} Available upon request.

\end{resume}
\end{document}

